---
title: "TT_Friends"
output: html_document
---
```{r}
# Load all the packages
pacman::p_load(pacman,dplyr,GGally, ggplot2, ggthemes, ggvis, httr, lubridate, plotly, rio, rmarkdown, shiny, stringer, tidyr, tidyverse)
#Packages to load everytime with pacman::p_load


```


```{r}
# Load all the Friends data
  friends <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-08/friends.csv')
friends_emotions <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-08/friends_emotions.csv')
friends_info <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-08/friends_info.csv')

```

```{r cars}
head(friends)
glimpse(friends)
```


```{r}
friends %>%
  count(speaker) %>%
  arrange(desc(n))
#Rachel Green has the most dialogue followed by Ross and Chandler 


 
```
## Create a dataframe with just the main cast and plot it
```{r}

main_cast <- friends %>%
  filter(speaker %in% c("Rachel Green", "Ross Geller", "Chandler Bing", "Monica Geller", "Joey Tribbiani", "Phoebe Buffay"))

ggplot(main_cast, aes(x = speaker)) + geom_bar() + coord_flip()

 
```

## Order the barchart

```{r}

main_cast <- friends %>%
  filter(speaker %in% c("Rachel Green", "Ross Geller", "Chandler Bing", "Monica Geller", "Joey Tribbiani", "Phoebe Buffay"))

# Use fct_infreq to order speakers by count then fct_rev to reverse the order
ggplot(main_cast, aes(x = fct_rev(fct_infreq(speaker)))) + geom_bar() + coord_flip()

 
```
## How does the main cast compare to all the side characters?
```{r}

friends %>% 
  #filter out Null values
  filter(!is.na(speaker)) %>%
  
  #use fct_collapse() to group the main cast together
  mutate(grouped_cast = fct_collapse(speaker, "Main Cast" = c("Rachel Green", "Ross Geller", "Chandler Bing", "Monica Geller", "Joey Tribbiani", "Phoebe Buffay"))) %>%
  
  #use fct_other():keep to group the side characters into Other
  mutate(grouped_cast = fct_other(grouped_cast, keep = c("Main Cast"))) %>%
  count(grouped_cast) %>%
  
  ggplot(aes( x = grouped_cast, y = n)) + geom_col() 
  


 
```
## Make a word cloud of the main cast's dialogue

First we install wordcloud2  
```{r}
install.packages("devtools")
 require(devtools)
devtools::install_github("lchiffon/wordcloud2") 


 
```
  

## Cleaning Our Text

Using the Text Mining library(tm) to create a corpus and clean our text from stop words 
```{r}
library(tm)

#make a corpus of all the main cast's dialogue
main_cast.corpus = Corpus(VectorSource(main_cast$text))

#Use tm_map to remove clean the text: strip whitespace, remove numbers, remove stop words, etc.
main_cast.corpus = main_cast.corpus %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace) %>%
  tm_map(content_transformer(tolower)) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(removeWords, stopwords("SMART")) %>%
  tm_map(removeWords, c("yeah", "dont", "gonna", "youre", "yknow", "hey")) #words that stopwords("english") misses
  


 
```
## Create Our Word Cloud Dataframe 

Note: I got an error about allocation when I first ran this code. If that happens on your machine check your set R memory limit via memory.limit() and remember that you can change it in the R console using memory.limit(size = ...)
```{r}

tdm = TermDocumentMatrix(main_cast.corpus) %>%
  as.matrix()
words = sort(rowSums(tdm), decreasing = TRUE)
df = data.frame(word = names(words), freq = words)
  
 
```

## Finally Generate Our WordCloud
```{r}
#Pass in the dataframe into wordcloud2
#Note: it's a lot of data this might take awhile 
wordcloud2(df)
  
 
```




